\textbf{Emergency Service Location Optimization in a Multi-Zone District based on Population Distribution}

### 2013-11-16 LaTeX/paper.tex
Refactoring assumptions/justifications

\section{Assumptions and Justifications}
\begin{enumerate}
    \item The travel times given are calculated from an optimal route from the center of the first
        zone to the center of ths econd. This excludes the possibility of reaching a zone faster
        via an indirect route from the direct, given one.
    \item The travel times given for travel from any zone to itself is the average
        of all the travel times of the different routes within that zone.
    \item The ratio between the time it takes inside a zone to travel toward a second zone,
        to the time it takes inside a zone to return from a second, is equal to the ratio
        between the travel time from the first zone to the second, and the travel time from the
        second to the first.
    \item
        Ambulances can only be placed in the very center of a zone. Because we do not know the
        spacial position of the zones relative to each other, we cannot consider the ambulances
        being closer to one zone or another.
    \item
        Partial ambulance coverage of a zone will be treated as imcomplete even coverage ove the entire
        zone. Because ambulances of ideal placement are unlikely to overlap in partial coverage, we assume
        that multiple ambulances will cover different areas of the zones, thus evening out coverage.
\end{enumerate}

@@

\subsection{Zone-to-Zone Population Dynamics}
An ambulance stationed in one zone may have full, partial, or no coverage of another zone. The population
that the ambulance can cover in a second zone from a first zone (not necessarily distinct), will be hereafter referred to as
zone-to-zone coverage.
\begin{description}
    \item[$A(t), B(t)$] Zones A and B are two zones separated by a gap. Each zone has a width and a population distribution
    \item[$Z_{AB}(t)$] Zone-to-zone coverage of  B from  A
    \item[$v$] required ambulance response time
    \item[$T_{AB}$] travel time from A to B, given
    \item[$T_{BA}$] travel time from B to A, given
    \item[$P_B$] total population of B
    \item[$F_B(s)$] the probability curve for differences in travel time within B
    \item[$T_{A^+}$] travel time inside of A traveling away from B
    \item[$T_{A^-}$] travel time inside of A traveling toward B
    \item[$T_{B^+}$] travel time inside of B traveling away from A
    \item[$T_{B^-}$] travel time inside of B traveling toward A
    \item[$a, b$] width of A and B respectively
    \item[$g$] width of the gap between A and B
\end{description}

%TODO: Graphical representation of origin and setup

The function for zone-to-zone coverage in respect to travel time can be written out as 
$$Z_{AB}(t) = P_B \int^v_{T_{AB} - \frac{b}{2}} B(t) dt$$
In order to find the width of zone B, b, we can take the probability curve of differences in travel time within B, $F_B(s)$, and find the average travel time within B. This is the average difference in travel time, and is equal to $T_{B+}$. 
$$T_{B+} = \int^{T_{AB}}_{T_{AB} - b} s F_B(s) ds$$

>>>>

\section{Assumptions and Justifications}
\begin{description}
    \item[1. Zone to Zone Travel] \hfill \\
    	The travel times given are calculated from an optimal route from the center of the first
        zone to the center of the second. This excludes the possibility of reaching a zone faster
        via an indirect route from the direct, given one.
    \item[2. Zone Interior Travel] \hfill \\
    	The travel times given for travel from any zone to itself is the average
        of all the travel times of the different routes within that zone.
    \item[3. Zone Directional Travel] \hfill \\
    	The ratio between the time it takes inside a zone to travel toward a second zone,
        to the time it takes inside a zone to return from a second, is equal to the ratio
        between the travel time from the first zone to the second, and the travel time from the
        second to the first.
    \item[4. Ambulance Placement] \hfill \\
        Ambulances can only be placed in the very center of a zone. Because we do not know the
        spacial position of the zones relative to each other, we cannot consider the ambulances
        being closer to one zone or another.
    \item[5. Partial Coverage] \hfill \\
        Partial ambulance coverage of a zone will be treated as imcomplete even coverage over the entire
        zone. Because ambulances of ideal placement are unlikely to overlap in partial coverage, we assume
        that multiple ambulances will cover different areas of the zones, thus evening out coverage.
\end{description}

@@

\subsection{Part 1?}
An ambulance stationed in one zone may have full, partial, or no coverage of another zone. The population
that the ambulance can cover in a second zone from a first zone (not necessarily distinct), will be hereafter referred to as
zone-to-zone coverage.
\begin{description}
    \item[$A(t), B(t)$] Zones A and B are two zones separated by a gap. Each zone has a width and a population distribution
    \item[$Z_{AB}(t)$] Zone-to-zone coverage of  B from  A
    \item[$v$] required ambulance response time
    \item[$T_{AB}$] travel time from A to B, given
    \item[$T_{BA}$] travel time from B to A, given
    \item[$P_B$] total population of B
    \item[$T_{A^+}$] travel time inside of A traveling away from B
    \item[$T_{A^-}$] travel time inside of A traveling toward B
    \item[$T_{B^+}$] travel time inside of B traveling away from A
    \item[$T_{B^-}$] travel time inside of B traveling toward A
    \item[$a, b$] width of A and B respectively
    \item[$g$] width of the gap between A and B
\end{description}

%TODO: Graphical representation of origin and setup
The function for zone-to-zone coverage in respect to travel time can be written out as 
$$Z_{AB}(t) = P_B * \int^v_{T_{AB} - \frac{b}{2}} B(t) dt$$
